Evaluating the Performance and Energy Efficiency of the \textsc{COSMO-ART} model system

### 2014-04-25 paper_enahpc14/Sec1:Related.tex
WS: revised
WS: proofread
Manuel's changes

While the  TOP500 list was  introduced over 20  years ago to  rank the
performance of HPC systems  worldwide, it's quite recently that energy
efficiency  become  a  critical  constraint  in the  way  to  exascale
computing.   Since 2007,  the Green500  power  measurement methodology
encourages the design,  procurement and management of energy-efficient
infrastuctures to contain performance in an affordable and competitive
power  envelope.   However,  the state-of-the-art  research  assessing
performance  and energy  efficiency  of applications  is still  pretty
scarce.

>>>>

While the  TOP500 list was  introduced over 20  years ago to  rank the
performance of HPC systems  worldwide, it is quite recently that energy
efficiency  become  a  critical  constraint  in the  way  to  exascale
computing.   Since 2007,  the Green500  power  measurement methodology
encourages the design,  procurement and management of energy-efficient
infrastuctures to contain performance in an affordable and competitive
power  envelope.   However,  the state-of-the-art  research  assessing
performance  and energy  efficiency  of applications  is still scarce.
